### 2019-08-21 paper/spad_single/sections/simulation.tex
Inpainting realsense data and working on the paper figures.

\subsection{Implementation Details}
\begin{itemize}
  \item Number of bins used, depth range, laser parameters, use of intensity
    image.
  \item Using
\end{itemize}
\paragraph{NYU Depth v2}
The NYU Depth v2 Dataset consists of 249 training and 215 testing scenes of
RGB-D data captured using a Microsoft Kinect. We used a version of DORN
pretrained according to \cite{Fu. et al} as our CNN.
\newpage
\begin{table*}
\begin{center}
\begin{tabular}{lccc|ccc}
  \toprule
    & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel $\downarrow$ & $log_{10} \downarrow$ \\
  \midrule
Eigen et. al. & 0.769 & 0.950 & 0.988 & 0.641 & 0.158 & - \\ 
Laina et. al.&0.811&0.953&0.988&0.573&0.127&0.055 \\
DORN&0.818&0.950&0.982&0.620&0.137&0.063 \\
  DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
Alhashim, Wonka (2019)&0.847&0.973&0.994&0.548(0.461)&0.123&0.053 \\
Alhashim, Wonka (2019) rescaled using GT depth"&0.888&\textbf{0.978}&\textbf{0.995}&\textbf{0.499}(0.409)&\textbf{0.106}&\textbf{0.045} \\
  \midrule
  Ours (raw depth counts) & \textbf{0.899} & 0.970 & 0.990 & 0.529 & 0.199 & 0.055 \\
  Ours (DORN) (intensity/falloff) & 0.835 & 0.953 & 0.984 & 0.521 & 0.129 & 0.060 \\
  Ours (DenseDepth) (intensity/falloff) & 0.867 & 0.974 & 0.994 & 0.445 & 0.114 & 0.050 \\
  \bottomrule
\end{tabular} 
\end{center}
\caption{Results on the NYU Depth v2 test set \cite{nyudepth}.}
\end{table*}
%%%
\begin{table*}
\begin{center}
\input{sections/figures/sim_table.tex}
\end{center}
\end{table*}
\begin{figure}
  \includegraphics[width=\textwidth/2]{sections/figures/comparison.jpeg}
  \caption{\textbf{Comparing our results with other methods}}
\end{figure}

>>>>

\subsection{Implementation Details}
\begin{itemize}
  \item Number of bins used, depth range, laser parameters, use of intensity
    image.
  \item Using
\end{itemize}
\paragraph{NYU Depth v2}
The NYU Depth v2 Dataset consists of 249 training and 215 testing scenes of
RGB-D data captured using a Microsoft Kinect. We used a version of DORN
pretrained according to \cite{Fu. et al} as our CNN.
\newpage
% \begin{table*}
% \begin{center}
% \begin{tabular}{lccc|ccc}
%   \toprule
%     & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel $\downarrow$ & $log_{10} \downarrow$ \\
%   \midrule
% Eigen et. al. & 0.769 & 0.950 & 0.988 & 0.641 & 0.158 & - \\ 
% Laina et. al.&0.811&0.953&0.988&0.573&0.127&0.055 \\
% DORN&0.818&0.950&0.982&0.620&0.137&0.063 \\
%   DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
% Alhashim, Wonka (2019)&0.847&0.973&0.994&0.548(0.461)&0.123&0.053 \\
% Alhashim, Wonka (2019) rescaled using GT depth"&0.888&\textbf{0.978}&\textbf{0.995}&\textbf{0.499}(0.409)&\textbf{0.106}&\textbf{0.045} \\
%   \midrule
%   Ours (raw depth counts) & \textbf{0.899} & 0.970 & 0.990 & 0.529 & 0.199 & 0.055 \\
%   Ours (DORN) (intensity/falloff) & 0.835 & 0.953 & 0.984 & 0.521 & 0.129 & 0.060 \\
%   Ours (DenseDepth) (intensity/falloff) & 0.867 & 0.974 & 0.994 & 0.445 & 0.114 & 0.050 \\
%   \bottomrule
% \end{tabular} 
% \end{center}
% \caption{Results on the NYU Depth v2 test set \cite{nyudepth}.}
% \end{table*}
%%%
\begin{table*}
\begin{center}
\input{sections/figures/sim_table.tex}
\caption{Simulated Results on NYU Depth v2. Bold indicates best performance for
  that metric, while underline indicates second best.}
\end{center}
\end{table*}

\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_18_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_21_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_25_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_194_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_285_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_42_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_52_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_53_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_103_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_224_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_226_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_352_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_362_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_379_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_107_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_187_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_140_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_244_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_527_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_529_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_529_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_219_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_329_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_346_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_616_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_390_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_412_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_420_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_428_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_457_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_468_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_477_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
%   \includegraphics[height=3cm]{sections/figures/comparison/densedepth_499_comparison.png}
%   \includegraphics[height=3cm]{sections/figures/comparison/densedepth_258_comparison.png}
%   \includegraphics[height=3cm]{sections/figures/comparison/densedepth_341_comparison.png}

% Densedepth:
% - Office: 18, 21
% - Bathroom: 25, 194, 285
% - Bookstore: 42
% - Kitchen: 52, 53, 103, 224, 226, 352, 362, 379
% - Office: 107, 187
% - Living Room: 140, 244, 527, 529
% - Dining Room: 219, 329, 346, 616
% - Bedroom: 390, 412, 420, 428, 457*, 468*, 477, 499
% Failure Cases: 258, 338(?), 341, 537 649 (minor)
% 
% DORN:
% - Office: 8, 14, 15, 23, 26
% - Living room: 63, 67, 140, 170, 522, 548, 569, 585, 633
% - Office: 105, 220, 252, 259* (interesting)
% - Kitchen: 178
% - Dining Room: 219
% - Bathroom: 280, 293, 313
% - Bedroom: 413, 477, 502
% 
% Failure Cases: 96, 266(?)

% \begin{figure}
%   \includegraphics[width=\textwidth/2]{sections/figures/comparison.jpeg}
%   \caption{\textbf{Comparing our results with other methods}}
% \end{figure}
